### 2025-01-10 article/Article.tex
final updates before resubmission

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Many laboratories use two-photon microscopy through commercial suppliers, or homemade designs of considerable complexity. The integrated nature of these systems complicates customization, troubleshooting, and \textcolor{blue}{training on the} principles of two-photon microscopy. Here, we present ``Twinkle'': a microscope for Two-photon Imaging in Neuroscience, and Kit for Learning and Education. It is a fully open, high performing and \textcolor{blue}{easy-to-set-up microscope that can effectively be used for both education and research}. The instrument features \textcolor{blue}{a $>1\text{ mm}$ field of view}, using a modern objective with \textcolor{blue}{3 mm} working distance and \textcolor{blue}{two inch diameter optics combined with GaAsP photomultiplier tubes} to maximize the fluorescence signal. We document our experiences using this system as a teaching tool in several two week long workshops, exemplify scientific use cases, and conclude with a broader note on the place of our work in the growing space of open-source scientific instrumentation.

@@

\section*{Introduction}
%
Two-photon microscopy\cite{Denk1990, Svoboda1997} \textcolor{blue}{is a key technology across the modern life sciences\cite{Zipfel2003}, for example, in physiology\cite{Ueki2020, Dunn2002}, cancer research \cite{Perry2012}, plant biology \cite{Cheung2010}, and neuroscience\cite{So2000, Helmchen2005}. New scientific use cases and technological improvements are published at a remarkable rate\cite{Luu2024}.} However, these instruments \textcolor{blue}{are often published without detailed building instructions and explanations}. This suggests the need for an \textcolor{blue}{easy-to-set-up microscope, at reasonable cost, that can be effectively used for education, dissemination, methods development and research.} We developed a high-performance and cost-effective two-photon microscope that can \textcolor{blue}{easily be produced} in many neuroscience laboratories. Reflecting its use for ``\textbf{TW}o-photon \textbf{I}maging in \textbf{N}euroscience, and \textbf{K}it for \textbf{L}earning and \textbf{E}ducation'', we chose the acronym Twinkle. In this article, we share our design, document the performance of the system, explore possible research applications, and report our experiences collected during several teaching workshops. \textcolor{blue}{Complete CAD drawings, bill of materials, optics simulations, and detailed building instructions are provided in the supplement.}

\section*{Materials and methods}
In two-photon laser-scanning microscopy\cite{Denk1990}, laser light is focused to a small excitation volume,  the ``focal point'', which is moved across the sample by the intermediary of resonant and galvanometric scanning mirrors. As the focal point probes different locations, different quantities of fluorescence light are produced by the sample. \textcolor{blue}{This light is collected by a sensitive detector in the form of an electronically measurable photocurrent.} An image is then formed, mapping the detector photocurrent values to the locations of excitation volume: low and high photocurrents, respectively, becoming dark and bright pixels. Central to two-photon fluorescence excitation is the light source: a femtosecond-pulsed infrared laser of sufficient pulse energy to achieve, when focused by an objective lens, a photon density high enough for simultaneous absorption of two photons by a fluorescent molecule. Here, we design an open and high-performing microscope that uses these principles. As such, we have made all optical and mechanical designs, electronics, bill of materials (BOM), CAD assembly, testing results, and relevant schematics open to the public. \textcolor{blue}{Excluding laser and optical table, the cost is around US-\$ 110k (2024). Including laser and table, the cost is around US-\$ 200k (2024).} A narrative of the design and the high-level view is presented here. For further details, we refer the reader to \nameref{S1_Appendix}. All code, figures and text, CAD designs, optics simulations, and BOM are available on  \url{https://github.com/BrainCOGS/Microscope} \textcolor{blue}{and on Zenodo \cite{Zenodo2024}.}

\subsection*{Design specifications}
We aimed for a mechanical and optical assembly using as many off-the-shelf components as possible, with only few custom aluminium parts that can be machined in any university machine shop. Our design  facilitates the adaptation for \invivo imaging by providing a large space for the organism and ancillary hardware. Our system is made cost-effective, in part, by the availability of femtosecond laser systems based on fiber technology. Operating at a fixed wavelength, these systems come at the fraction of the cost of a tunable Ti:Sapphire laser \cite{Bueno2019}.\newline
More specifically, we aimed for (1) $\gtrapprox20\text{ cm}$ of free space around the objective in all directions to aid integration of the microscope with various peripheral equipment such as behavior boxes or a sample stage, and (2) imaging on a  $\approx 700\times 700\text{ \textmu m}^2$ minimum size field of view which is typical for imaging brain tissue at cellular resolution. (3) Compared to earliest open designs\cite{Rosenegger2014, Mayrhofer2015}, our system can make use of the large Numerical Aperture (NA) of  modern long-working-distance objectives to collect more fluorescence, but requires to adapt our design to their larger back apertures \cite{Janelia2024}.\newline
An overview of the microscope is shown in Fig.~\ref{fig1}. Fig.~\ref{fig1}A,B shows the system as a cartoon. Full details will be provided below. In short, we chose a 920 nm femtosecond pulsed laser, whose beam diameter is extended by a $2\times$ magnification telescope, before it reaches the scanning mirrors. The scanning mirrors are purchased as a mount-assembled set. Located as close as possible to each other, as we will see in the alignment procedure, neither of them can be exactly positioned in the focal plane of the scan lens. The choice of mounted scanners simplifies the design and construction, but leads to optical distortions across the field of view. \textcolor{blue}{We found that this distortion does not exceed 5\% in our design (see below)}. The combined scan and tube lenses magnify the beam further to fill the objective's back aperture. Fluorescence from the specimen is then collected and brought to the aperture of two GaAsP photomultiplier tubes with suitable color filters. Fig.~\ref{fig1}C shows the CAD design of the entire assembly with important parts of the optical path labeled. Fig.~\ref{fig1}D shows an annotated picture of the microscope head. Notice that compared to the cartoon in Fig.~\ref{fig1}A,B, the optical path is folded with several mirrors. These mirrors make the microscope assembly more compact.

\begin{figure}[!t]
    \includegraphics[width=\textwidth]{fig1.jpg}
    \caption{{\bf System overview.} \textbf{A)} \textcolor{blue}{Key components of the microscope head. Shaded colors illustrate beam deflection angles. \textbf{B)} Cartoon of the beam conditioning components. First the beam is split by 50\%, the intensity adjusted with an electro-optic modulator (EOM) and the beam width with a telescope before entering the microscope head. \textbf{C)} 3D drawing of the full microscope, highlighting beam conditioning subsystem (blue) and the microscope head (yellow). For scale, the spacing between two holes on the optical table is 1 inch or 2.5 cm. \textbf{D)} Photograph of the microscope head with key elements labeled. This section is visible in panel A.}}
    \label{fig1}
\end{figure}

\subsection*{Assembly on the table}
Various components are used between the laser and the microscope head to condition the beam, and  for intensity control, Fig.~\ref{fig1}B. Out of the laser head, the beam first encounters a waveplate (AHWP10M-980, Thorlabs). This is a birefringent crystal that can rotate the linear polarization of the laser to any angle. Next, the beam travels through a polarizing beamsplitter cube (PBS103, Thorlabs). This splits the beam into two orthogonal polarization components whose relative intensity is adjusted by the orientation of the waveplate. We set the orientation of the waveplate to split the beam into equal power components, the second one being eventually used for a second microscope installed on the other extremity of the table. In the cartoon, this second beam is sent to a beam block (LB1, Thorlabs). \textcolor{blue}{We want to stress that this beam-splitting hardware is optional. However, modern lasers have enough power to supply two microscopes at the same time. It is therefore often strategic to split the beam into two beams, with half of the intensity each, to allow one laser (the most expensive component) to power two systems.} Next, the beam passes through an electro-optic modulator (EOM), a Pockels cell (350-80-LA-02, Conoptics). This device allows rapid and electronic control of the laser's power level. It uses a crystal whose refractive index is controlled by an external electric field, combined with a polarizer. This can be thought of as a voltage-controlled wave plate, in which the electric field controls how much light travels through the polarizer. Next, the beam travels through an open mechanical 6 mm diameter shutter (LS6S2ZM1, Vincent Associates). When closed, the laser reflected on the shutter reflective blades is sent to another beam block. Beam blocks are not perfect absorber, so we can use advantageously the weak back scattered light from the beam block to calibrate the Pockels cell. In our set-up, a photodiode (PDA36A2, Thorlabs) is thus facing the beam block. Following the shutter, the beam travels though a $2\times$ telescope (GBE02-B, Thorlabs) doubling its diameter. Past the telescope, the beam is then reflected off several mirrors in a periscope configuration before entering a custom aluminium box housing, mounted to a 95 mm optical rail (XT95 series, Thorlabs), that houses the two scanning mirrors (CRS8K/6215H scanning mirror set, Novanta), shown in blue in Fig.~\ref{fig1}D. Leaving the scanners, the beam then travels first through the scan lens (green) and tube lens (red), passes through the long pass dichroic mirror of the collection box assembly (yellow) and finally the objective (cyan). The design of these components is covered in the next paragraphs. The steering mirrors in our system are all P01 silver protected mirrors from Thorlabs. Silver mirrors contribute minimally to dispersion which is inevitable when light travels through various optical components. Limiting the dispersion makes it possible to correct for it with the laser's built-in dispersion compensation.

@@

\subsection*{Mechanical design}
Our microscope was mounted on a 16 inch thick optical table. The design was done in CAD Inventor and Fusion 360 (Autodesk), and the results shown in Fig.~\ref{fig1}C. The aim was a mechanical assembly that uses as few custom parts as possible. This is relatively easy to achieve for the excitation path, but hardly practical for the collection system which require to be both efficient and light tight. The components shown in the CAD files can be assembled and aligned by an experienced researcher in a few days. When used for teaching, a careful assembly and alignment is viable with about a week of work. \textcolor{blue}{When set up on an imperial-unit table, the system can comfortably be built on $4\times4 \text{ ft}^2$. The microscope documented here was built on a $4\times8\text{ ft}^2$ table, shared with a second microscope. In metric units, our microscope has a footprint of $\approx 1.5\text{ m}^2$. In other words, a standard $1.2\times2.5\text{ m}^2$ table can house two of the systems described here.} The beam-splitting hardware \textcolor{blue}{used for this arrangement} is shown in Fig.~\ref{fig1}B,C as well.\newline
The custom mechanical components (e.g. the light-tight aluminium housing of the collection optics) were built in the university's machine shop from aluminium stock or Thorlabs parts. Some parts have tight tolerances which suggests manufacturing in a professional machine shop is preferred. If useful for training, this could however be done by students. An example are the aluminium parts that hold the large dichroic mirrors and optical filters in the collection optics. After drilling the apertures for light to pass through, little metal is left on the part which can potentially lead to warping and distortions if not machined with precision.\newline
Finally, we want to emphasize the difference between a theoretically optimal design in Zemax and finite tolerances in real-world optomechanical parts. It is key for a good microscope design to be robust against such errors. In our design, the objective is fixed, while the mirrors, the tube and scan lens assemblies, and the scanning mirrors can be re-positioned along the optical axis for alignment. This allows the mechanical components sufficient degrees of freedom to optically align all key parts of the microscope. In the supplement, we go through this alignment procedure in detail.

\subsection*{Scanners power supplies and controllers enclosure}
The scanning mirrors are active components. They are controlled by two circuit boards supplied with external power. The driver board of the resonant scanner does not dissipate much heat, but the driver of the slow galvanometer can become warm in normal operation. This heat needs to be dissipated. We mount the circuit boards in a custom electronics box (Gold Box, Acopian), making sure to use heat transfer compound between the circuit boards and the aluminium box, and to mount them securely together with screws. At time of purchase, we requested the controller of the slow galvanometer to be configured for usage at $\pm 28\text{ V}$ (the manufacturer default is $\pm 24\text{ V}$). In our experience, this  improves dynamical properties. The controller requires three supply lines, -28 V, 0 V, and +28 V. \textcolor{blue}{To provide these voltages, we used a power supply with two galvanically isolated and adjustable outputs (not every power supply supports this function). The voltage of each of the two channels was set to +28 V. To produce the three supplies, we used these two channels in series. In other words, we connect the positive terminal of the first channel to the negative terminal of the second channel. As the channels are otherwise not connected to a common ground (this is meant with the words ``galvanically isolated''), this does not produce a short circuit. Instead, this link effectively provides a new reference point, relative to which the first supply produces a negative -28 V supply, and the second supply produces the +28 V supply. More details are provided in the supplement.} The second power supply provides 12 V for the resonant scanner. It is beneficial to choose a power supply that can stably produce these voltages for years. We have made good experiences with Agilent E3630A, and the Instek GPD-3303D. Importantly, double check the power supplies with a good multimeter before connecting the driver boards. Please also see \nameref{S1_Appendix} for a detailed illustration.

@@

\subsection*{Ancillary hardware}
Our microscope is controlled with ScanImage \cite{Pologruto2003} running on a Windows PC equipped with a data acquisition system (DAQ), both from the same supplier (MBF Bioscience). For the work demonstrated here, we used a fixed-wavelength femtosecond laser systems, based on fiber technology (e.g.\cite{Bueno2019,Limpert2006,Wise2012,Young2015}). \textcolor{blue}{These devices come at $\approx 1/3$ of the cost of a Ti:Sapphire system, and take up significantly less real estate on the optical table.} Our laser, \textcolor{blue}{an Alcor 920 manufactured by Spark Lasers}, was controlled with the same PC as ScanImage through a USB connection. As the beam travels through a number of crystals, lenses, and mirrors with various chromatic properties, significant dispersion is introduced which increases pulse duration, reducing the two-photon absorption efficiency. It is possible to compensate for the group-delay dispersion of the microscope by giving the short-wavelength components a sufficient head start so that blue and red components arrive at the sample at the same time. We found, empirically, that the built-in group velocity dispersion compensation of the laser was more than sufficient to tune the system to an optimum, which we found close to $\varphi=-20200\pm170\text{ fs}^2$. Details of this measurement, and some theory, are provided below as a teaching example (cf. Fig.~\ref{fig9}). Regarding light transmission, we found the Spark laser to produce $\approx 2.1\text{ W}$ of light. After the half-wave plate and beamsplitter cube, $\approx 1.0\text{ W}$ enter the Pockels cell (cf. Fig.~\ref{fig1}B). The Pockels cell is rotated so that the control voltage produces the largest dynamic range of transmitted laser power (we go through the alignment procedure in depth below). At maximum transmission setting of the Pockels cell, we obtain $\approx 260\text{ mW}$ below the objective, a large value, as it is exceeding the maximum recommended power for cortical imaging in mice \cite{Song2017}. All pictures presented in this article were obtained with $\approx 15\text{ mW}$ below the objective.

\subsection*{Ethics statement}
\textcolor{blue}{Some of the data presented here were obtained from animals. Our work was conducted according to internationally accepted standards and we followed all laws and regulations about animal research in the United States and Germany. We used vertebrate animals in the form of GCaMP6f expressing transgenic Zebrafish (\textit{Danio rerio}) for \invivo imaging. Fish were bred and housed at the Princeton Neuroscience Institute. We used five day old larvae immobilized in 2\% low melting point Agarose in E3 medium. Larvae were sacrificed after the imaging sessions. As required by law, we have obtained prior approval by the Institutional Animal Care and Use Committee at Princeton University under Protocol Number 2033. Further \invivo imaging work was done in the adult fruit fly (\textit{Drosophila melanogaster}). In the United States, work in lower-level invertebrate species like the fruit fly does not require approval by the Institutional Animal Care and Use Committee. We also imaged a previously prepared fixed and stained histological sample obtained from a Wistar rat (\textit{Rattus norvegicus}). This specific sample was made by one of us during their PhD\cite{Schottdorf2018}. The animal was bred in the animal house of the Max Planck Institute for Experimental Medicine according to European and German guidelines for experimental animals, and work was carried out with authorization of the responsible federal state authority. Finally, we imaged plant material from the common Dandilion (\textit{Taraxacum officinale}) \textit{in vivo}. This experiment does not require ethics approval in the United States.}

@@

Twinkle was assembled, disassembled, and reassembled three times by different groups of researchers and students. In the following paragraphs, we summarize our experiences, and produce two examples for what we consider useful learning experiences for two-photon microscopy. \textcolor{blue}{The detailed building instructions and additional information are available the supplement, \nameref{S1_Appendix}}.\newline

@@

In this article, we have covered the design, building, and alignment of a two-photon microscope. We then assessed its performance and demonstrated several possible use cases, from plant physiology over material science to neuroscience. \textcolor{blue}{In the following paragraphs, we will expand on some recent scientific use cases of two-photon microscopy, discuss improvements to the design, elaborate on its use for education,} and conclude with a note about our instrument in the growing space of open source scientific instrumentation.

\subsection*{Scientific use cases}
\textcolor{blue}{Based on its unique ability to image with high resolution and limited photo damage deep into scattering samples, two-photon microscopy became an important tool across the life sciences. For example, \textit{ex vivo}, two-photon microscopy can monitor, in three dimensions, both the living and cornified keratinocytes of the epidermis, the collagen/elastin fibers in the dermal layer of the skin \cite{So1998} or the dynamics of quiescent skeletal muscle stem cells embedded in the muscle at cellular resolution \cite{Ma2024}. \textit{In vivo}, two-photon microscopy allows to monitor the dynamics of viral infections in the lung \cite{Ueki2020}, cell vitality and apoptosis, fluid transport, receptor-mediated endocytosis, blood flow, and leukocyte trafficking in the kidney \cite{Dunn2002}, 
blood vascular hemodynamics in the thymus \cite{Seyedhassantehrani2024}, stem cells in the skin \cite{Huang2017}, produces new insights into cancer \textit{ex vivo} and \textit{in vivo} \cite{Perry2012}, and even entered clinical practice \cite{Konig2007}.\newline

>>>>

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Many laboratories use two-photon microscopy through commercial suppliers, or homemade designs of considerable complexity. The integrated nature of these systems complicates customization, troubleshooting, and \textcolor{black}{training on the} principles of two-photon microscopy. Here, we present ``Twinkle'': a microscope for Two-photon Imaging in Neuroscience, and Kit for Learning and Education. It is a fully open, high performing and \textcolor{black}{easy-to-set-up microscope that can effectively be used for both education and research}. The instrument features \textcolor{black}{a $>1\text{ mm}$ field of view}, using a modern objective with \textcolor{black}{3 mm} working distance and \textcolor{black}{2 inch diameter optics combined with GaAsP photomultiplier tubes} to maximize the fluorescence signal. We document our experiences using this system as a teaching tool in several two week long workshops, exemplify scientific use cases, and conclude with a broader note on the place of our work in the growing space of open scientific instrumentation.

@@

\section*{Introduction}
%
Two-photon microscopy\cite{Denk1990, Svoboda1997} \textcolor{black}{is a key technology across the modern life sciences\cite{Zipfel2003}, for example, in physiology\cite{Ueki2020, Dunn2002}, cancer research \cite{Perry2012}, plant biology \cite{Cheung2010}, and neuroscience\cite{So2000, Helmchen2005}. New scientific use cases and technological improvements are produced at a remarkable rate\cite{Luu2024}.} However, these instruments \textcolor{black}{are often published without detailed building instructions and explanations}. This suggests the need for an \textcolor{black}{easy-to-set-up microscope, at reasonable cost, that can be effectively used for education, dissemination, methods development and research.} We developed a high-performance and cost-effective two-photon microscope that can \textcolor{black}{easily be produced} in many neuroscience laboratories. Reflecting its use for ``\textbf{TW}o-photon \textbf{I}maging in \textbf{N}euroscience, and \textbf{K}it for \textbf{L}earning and \textbf{E}ducation'', we chose the acronym Twinkle. In this article, we share our design, document the performance of the system, explore possible research applications, and report our experiences collected during several teaching workshops. \textcolor{black}{Complete CAD drawings, bill of materials, optics simulations, and detailed building instructions are provided in the supplement.}

\section*{Materials and methods}
In two-photon laser-scanning microscopy\cite{Denk1990}, laser light is focused to a small excitation volume,  the ``focal point'', which is moved across the sample by the intermediary of resonant and galvanometric scanning mirrors. As the focal point probes different locations, different quantities of fluorescence light are produced by the sample. \textcolor{black}{This light is collected by a sensitive detector in the form of an electronically measurable photocurrent.} An image is then formed, mapping the detector photocurrent values to the locations of excitation volume: low and high photocurrents, respectively, becoming dark and bright pixels. Central to two-photon fluorescence excitation is the light source: a femtosecond-pulsed infrared laser of sufficient pulse energy to achieve, when focused by an objective lens, a photon density high enough for simultaneous absorption of two photons by a fluorescent molecule. Here, we design an open and high-performing microscope that uses these principles. As such, we have made all optical and mechanical designs, electronics, bill of materials (BOM), CAD assembly, testing results, and relevant schematics open to the public. \textcolor{black}{Excluding laser and optical table, the cost is around US-\$ 110k (2024). Including laser and table, the cost is around US-\$ 200k (2024).} A narrative of the design and the high-level view is presented here. For further details, we refer the reader to \nameref{S1_Appendix}. All code, figures and text, CAD designs, optics simulations, and BOM are available on  \url{https://github.com/BrainCOGS/Microscope} \textcolor{black}{and on Zenodo \cite{Zenodo2024}.}

\subsection*{Design specifications}
We aimed for a mechanical and optical assembly using as many off-the-shelf components as possible, with only few custom aluminium parts that can be machined in any university machine shop. Our design  facilitates the adaptation for \invivo imaging by providing a large space for the organism and ancillary hardware. Our system is made cost-effective, in part, by the availability of femtosecond laser systems based on fiber technology. Operating at a fixed wavelength, these systems come at the fraction of the cost of a tunable Ti:Sapphire laser \cite{Bueno2019}.\newline
More specifically, we aimed for (1) $\gtrapprox20\text{ cm}$ of free space around the objective in all directions to aid integration of the microscope with various peripheral equipment such as behavior boxes or a sample stage, and (2) imaging on a  $\approx 700\times 700\text{ \textmu m}^2$ minimum size field of view which is typical for imaging brain tissue at cellular resolution. (3) Compared to earliest open designs\cite{Rosenegger2014, Mayrhofer2015}, our system can make use of the large Numerical Aperture (NA) of  modern long-working-distance objectives to collect more fluorescence, but requires to adapt our design to their larger back apertures \cite{Janelia2024}.\newline
An overview of the microscope is shown in Fig.~\ref{fig1}. Fig.~\ref{fig1}A,B shows the system as a cartoon. Full details will be provided below. In short, we chose a 920 nm femtosecond pulsed laser, whose beam diameter is extended by a $2\times$ magnification telescope, before it reaches the scanning mirrors. The scanning mirrors are purchased as a mount-assembled set. Located as close as possible to each other, as we will see in the alignment procedure, neither of them can be exactly positioned in the focal plane of the scan lens. The choice of mounted scanners simplifies the design and construction, but leads to optical distortions across the field of view. \textcolor{black}{We found that this distortion does not exceed 5\% in our design (see below)}. The combined scan and tube lenses magnify the beam further to fill the objective's back aperture. Fluorescence from the specimen is then collected and brought to the aperture of two GaAsP photomultiplier tubes with suitable color filters. Fig.~\ref{fig1}C shows the CAD design of the entire assembly with important parts of the optical path labeled. Fig.~\ref{fig1}D shows an annotated picture of the microscope head. Notice that compared to the cartoon in Fig.~\ref{fig1}A,B, the optical path is folded with several mirrors. These mirrors make the microscope assembly more compact.

\begin{figure}[!t]
    \includegraphics[width=\textwidth]{fig1.jpg}
    \caption{{\bf System overview.} \textbf{A)} \textcolor{black}{Key components of the microscope head. Shaded colors illustrate beam deflection angles. \textbf{B)} Cartoon of the beam conditioning components. First the beam is split by 50\%, the intensity adjusted with an electro-optic modulator (EOM) and the beam width with a telescope before entering the microscope head. \textbf{C)} 3D drawing of the full microscope, highlighting beam conditioning subsystem (blue) and the microscope head (yellow). For scale, the spacing between two holes on the optical table is 1 inch or 2.5 cm. \textbf{D)} Photograph of the microscope head with key elements labeled. This section is visible in panel A.}}
    \label{fig1}
\end{figure}

\subsection*{Assembly on the table}
Various components are used between the laser and the microscope head to condition the beam, and  for intensity control, Fig.~\ref{fig1}B. Out of the laser head, the beam first encounters a waveplate (AHWP10M-980, Thorlabs). This is a birefringent crystal that can rotate the linear polarization of the laser to any angle. Next, the beam travels through a polarizing beamsplitter cube (PBS103, Thorlabs). This splits the beam into two orthogonal polarization components whose relative intensity is adjusted by the orientation of the waveplate. We set the orientation of the waveplate to split the beam into equal power components, the second one being eventually used for a second microscope installed on the other extremity of the table. In the cartoon, this second beam is sent to a beam block (LB1, Thorlabs). \textcolor{black}{We want to stress that this beam-splitting hardware is optional. However, modern lasers have enough power to supply two microscopes at the same time. It is therefore often strategic to split the beam into two beams, with half of the intensity each, to allow one laser (the most expensive component) to power two systems.} Next, the beam passes through an electro-optic modulator (EOM), a Pockels cell (350-80-LA-02, Conoptics). This device allows rapid and electronic control of the laser's power level. It uses a crystal whose refractive index is controlled by an external electric field, combined with a polarizer. This can be thought of as a voltage-controlled wave plate, in which the electric field controls how much light travels through the polarizer. Next, the beam travels through an open mechanical 6 mm diameter shutter (LS6S2ZM1, Vincent Associates). When closed, the laser reflected on the shutter reflective blades is sent to another beam block. Beam blocks are not perfect absorber, so we can use advantageously the weak back scattered light from the beam block to calibrate the Pockels cell. In our set-up, a photodiode (PDA36A2, Thorlabs) is thus facing the beam block. Following the shutter, the beam travels though a $2\times$ telescope (GBE02-B, Thorlabs) doubling its diameter. Past the telescope, the beam is then reflected off several mirrors in a periscope configuration before entering a custom aluminium box housing, mounted to a 95 mm optical rail (XT95 series, Thorlabs), that houses the two scanning mirrors (CRS8K/6215H scanning mirror set, Novanta), shown in blue in Fig.~\ref{fig1}D. Leaving the scanners, the beam then travels first through the scan lens (green) and tube lens (red), passes through the long pass dichroic mirror of the collection box assembly (yellow) and finally the objective (cyan). The design of these components is covered in the next paragraphs. The steering mirrors in our system are all P01 silver protected mirrors from Thorlabs. Silver mirrors contribute minimally to dispersion which is inevitable when light travels through various optical components. Limiting the dispersion makes it possible to correct for it with the laser's built-in dispersion compensation.

@@

\subsection*{Mechanical design}
Our microscope was mounted on a 16 inch thick optical table. The design was done in CAD Inventor and Fusion 360 (Autodesk), and the results shown in Fig.~\ref{fig1}C. The aim was a mechanical assembly that uses as few custom parts as possible. This is relatively easy to achieve for the excitation path, but hardly practical for the collection system which require to be both efficient and light tight. The components shown in the CAD files can be assembled and aligned by an experienced researcher in a few days. When used for teaching, a careful assembly and alignment is viable with about a week of work. \textcolor{black}{When set up on an imperial-unit table, the system can comfortably be built on $4\times4 \text{ ft}^2$. The microscope documented here was built on a $4\times8\text{ ft}^2$ table, shared with a second microscope. In metric units, our microscope has a footprint of $\approx 1.5\text{ m}^2$. In other words, a standard $1.2\times2.5\text{ m}^2$ table can house two of the systems described here.} The beam-splitting hardware \textcolor{black}{used for this arrangement} is shown in Fig.~\ref{fig1}B,C as well.\newline
The custom mechanical components (e.g. the light-tight aluminium housing of the collection optics) were built in the university's machine shop from aluminium stock or Thorlabs parts. Some parts have tight tolerances which suggests manufacturing in a professional machine shop is preferred. If useful for training, this could however be done by students. An example are the aluminium parts that hold the large dichroic mirrors and optical filters in the collection optics. After drilling the apertures for light to pass through, little metal is left on the part which can potentially lead to warping and distortions if not machined with precision.\newline
Finally, we want to emphasize the difference between a theoretically optimal design in Zemax and finite tolerances in real-world optomechanical parts. It is key for a good microscope design to be robust against such errors. In our design, the objective is fixed, while the mirrors, the tube and scan lens assemblies, and the scanning mirrors can be re-positioned along the optical axis for alignment. This allows the mechanical components sufficient degrees of freedom to optically align all key parts of the microscope. In the supplement, we go through this alignment procedure in detail.

\subsection*{Scanners power supplies and controllers enclosure}
The scanning mirrors are active components. They are controlled by two circuit boards supplied with external power. The driver board of the resonant scanner does not dissipate much heat, but the driver of the slow galvanometer can become warm in normal operation. This heat needs to be dissipated. We mount the circuit boards in a custom electronics box (Gold Box, Acopian), making sure to use heat transfer compound between the circuit boards and the aluminium box, and to mount them securely together with screws. At time of purchase, we requested the controller of the slow galvanometer to be configured for usage at $\pm 28\text{ V}$ (the manufacturer default is $\pm 24\text{ V}$). In our experience, this  improves dynamical properties. The controller requires three supply lines, -28 V, 0 V, and +28 V. \textcolor{black}{To provide these voltages, we used a power supply with two galvanically isolated and adjustable outputs (not every power supply supports this function). The voltage of each of the two channels was set to +28 V. To produce the three supplies, we used these two channels in series. In other words, we connect the positive terminal of the first channel to the negative terminal of the second channel. As the channels are otherwise not connected to a common ground (this is meant with the words ``galvanically isolated''), this does not produce a short circuit. Instead, this link effectively provides a new reference point, relative to which the first supply produces a negative -28 V supply, and the second supply produces the +28 V supply. More details are provided in the supplement.} The second power supply provides 12 V for the resonant scanner. It is beneficial to choose a power supply that can stably produce these voltages for years. We have made good experiences with Agilent E3630A, and the Instek GPD-3303D. Importantly, double check the power supplies with a good multimeter before connecting the driver boards. Please also see \nameref{S1_Appendix} for a detailed illustration.

@@

\subsection*{Ancillary hardware}
Our microscope is controlled with ScanImage \cite{Pologruto2003} running on a Windows PC equipped with a data acquisition system (DAQ), both from the same supplier (MBF Bioscience). For the work demonstrated here, we used a fixed-wavelength femtosecond laser systems, based on fiber technology (e.g.\cite{Bueno2019,Limpert2006,Wise2012,Young2015}). \textcolor{black}{These devices come at $\approx 1/3$ of the cost of a Ti:Sapphire system, and take up significantly less real estate on the optical table.} Our laser, \textcolor{black}{an Alcor 920 manufactured by Spark Lasers}, was controlled with the same PC as ScanImage through a USB connection. As the beam travels through a number of crystals, lenses, and mirrors with various chromatic properties, significant dispersion is introduced which increases pulse duration, reducing the two-photon absorption efficiency. It is possible to compensate for the group-delay dispersion of the microscope by giving the short-wavelength components a sufficient head start so that blue and red components arrive at the sample at the same time. We found, empirically, that the built-in group velocity dispersion compensation of the laser was more than sufficient to tune the system to an optimum, which we found close to $\varphi=-20200\pm170\text{ fs}^2$. Details of this measurement, and some theory, are provided below as a teaching example (cf. Fig.~\ref{fig9}). Regarding light transmission, we found the Spark laser to produce $\approx 2.1\text{ W}$ of light. After the half-wave plate and beamsplitter cube, $\approx 1.0\text{ W}$ enter the Pockels cell (cf. Fig.~\ref{fig1}B). The Pockels cell is rotated so that the control voltage produces the largest dynamic range of transmitted laser power (we go through the alignment procedure in depth below). At maximum transmission setting of the Pockels cell, we obtain $\approx 260\text{ mW}$ below the objective, a large value, as it is exceeding the maximum recommended power for cortical imaging in mice \cite{Song2017}. All pictures presented in this article were obtained with $\approx 15\text{ mW}$ below the objective.

\subsection*{Ethics statement}
\textcolor{black}{Some of the data presented here were obtained from animals. Our work was conducted according to internationally accepted standards and we followed all laws and regulations about animal research in the United States and Germany. We used vertebrate animals in the form of GCaMP6f expressing transgenic Zebrafish (\textit{Danio rerio}) for \invivo imaging. Fish were bred and housed at the Princeton Neuroscience Institute. We used five day old larvae immobilized in 2\% low melting point Agarose in E3 medium. Larvae were sacrificed after the imaging sessions. As required by law, we have obtained prior approval by the Institutional Animal Care and Use Committee at Princeton University under Protocol Number 2033. Further \invivo imaging work was done in the adult fruit fly (\textit{Drosophila melanogaster}). In the United States, work in lower-level invertebrate species like the fruit fly does not require approval by the Institutional Animal Care and Use Committee. We also imaged a previously prepared fixed and stained histological sample obtained from a Wistar rat (\textit{Rattus norvegicus}). This specific sample was made by one of us during their PhD\cite{Schottdorf2018}. The animal was bred in the animal house of the Max Planck Institute for Experimental Medicine according to European and German guidelines for experimental animals, and work was carried out with authorization of the responsible federal state authority. Finally, we imaged plant material from the common Dandilion (\textit{Taraxacum officinale}) \textit{in vivo}. This experiment does not require ethics approval in the United States.}

@@

Twinkle was assembled, disassembled, and reassembled three times by different groups of researchers and students. In the following paragraphs, we summarize our experiences, and produce two examples for what we consider useful learning experiences for two-photon microscopy. \textcolor{black}{The detailed building instructions and additional information are available the supplement, \nameref{S1_Appendix}}.\newline

@@

In this article, we have covered the design, building, and alignment of a two-photon microscope. We then assessed its performance and demonstrated several possible use cases, from plant physiology over material science to neuroscience. \textcolor{black}{In the following paragraphs, we will expand on some recent scientific use cases of two-photon microscopy, discuss improvements to the design, elaborate on its use for education,} and conclude with a note about our instrument in the growing space of open source scientific instrumentation.
